\documentclass[letterpaper,11pt]{article}
\usepackage[scale=0.9]{geometry}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{mdframed}

\newcolumntype{Y}{>{\centering\arraybackslash}X}  
\setlength\parindent{0pt}
\pagestyle{empty}

\begin{document}
\begin{tabularx}{\linewidth}{@{}lYcr@{}}                                                                      \\
  \multicolumn{4}{c}{\textbf{\Huge{James Kavanaugh}}}                                           \\
  \vspace{-10px}                                                                       &   &  & \\
  \hline
  \vspace{-10px}                                                                       &   &  & \\
  \faEnvelope{ \href{mailto:jkav@northslopesoftware.com}{jkav@northslopesoftware.com}} &
  \faPhone{ 253-209-9718}                                                              &
  \faLinkedin{ \href{https://linkedin.com/in/jkav3}{linkedin.com/in/jkav3}}            &
  \faGithub{ \href{https://github.com/dangerginger}{github.com/dangerginger}}                   \\
\end{tabularx}

\begin{mdframed}[backgroundcolor=gray!20,linewidth=0pt]
  \centering
  \textbf{\Large{Software Engineer}}
\end{mdframed}

\begin{center}
  \emph{Skilled, bilingual software engineer and proven leader with 20 years experience leading high-performance teams.}
\end{center}

\vspace{-10px}
\section*{Projects}
\hrule
\begin{itemize}[leftmargin=*,nosep]
  \item \textbf{Marine construction permitting system}: Client relationship management (CRM) application implemented with Typescript, React, AWS, websockets, and MongoDB to manage multi-year permitting processes.
        %\item \textbf{Request for Quote ERP Module}: Typescript and React enterprise resource planning (ERP) application with cloud-native AWS backend to streamline vendor quotes and purchasing for construction companies.
  \item \textbf{Web socket framework}: Typescript and Node.js web socket framework with message schema validation to enable real-time synchronization of web applications and maintain data consistency.
  \item \textbf{Encrypted synthetic data research (ongoing)}: Python and C++ based research using homomorphic encryption and differential privacy to maintain privacy of sensitive datasets while generating synthetic data.
  \item \textbf{Computer vision application (ongoing)}: C++, OpenCV and Tensorflow models to monitor RTSP camera streams, with macOS and tvOS client applications to view home security camera and insights.
        %\item \textbf{Space Time}: Native iOS and watchOS application with AWS Amplify and RDS backend to help users visualize time according to atomic time instead of as a cycle.
\end{itemize}

\vspace{-10px}
\section*{Experience}
\hrule
\begin{tabularx}{\linewidth}{@{}Xlr}
  \textbf{President and CEO (Owner)}                                              & North Slope Software                                  & 2022-2024      \\
  \multicolumn{3}{@{}m{\linewidth}@{}}{%
  \begin{itemize}[leftmargin=*,nosep]
    \item Sold, designed, and implemented a client relationship management system for a marine construction company.
    \item Responsible for business development, user experience design, software development, and DevOps.
    \item Designed, and implemented an enterprise resource planning software-as-a-service (SaaS) product.
  \end{itemize}}                                          \\
  \vspace{-10px}                                                                  & \vspace{-10px}                                        & \vspace{-10px} \\

  \textbf{U.S. Army Special Forces ``Green Berets''}                              & 1\textsuperscript{st} Special Forces Group (Airborne) & 2004-2024      \\

  \multicolumn{1}{|l}{\textbf{Indo-Pacfic Regional Program Manager}}              & Washington and overseas                               & 2020-2024      \\
  \multicolumn{3}{@{}|m{\linewidth}@{}}{%
  \begin{itemize}[leftmargin=*,nosep]
    \item Led a diverse, multifunctional staff to manage joint special operations teams in seven Asian countries.
    \item Mentored and developed leaders and technicians on high-performing teams to achieve strategic objectives.
    \item Responsible for written communication and briefings to synchronize operations with senior leaders' intent.
  \end{itemize}}                                          \\
  \vspace{-10px}                                                                  & \vspace{-10px}                                        & \vspace{-10px} \\

  \multicolumn{1}{|l}{\textbf{Special Forces Operations Manager (18Z)}}           & Washington and overseas                               & 2018-2020      \\
  \multicolumn{3}{@{}|m{\linewidth}@{}}{%
  \begin{itemize}[leftmargin=*,nosep]
    \item Managed a high-performance, multifunctional, and highly specialized special forces detachment.
    \item Responsible for training, mentorship, and professional development for a Special Forces operational detachment.
  \end{itemize}}                                     \\
  \vspace{-10px}                                                                  & \vspace{-10px}                                        & \vspace{-10px} \\

  \multicolumn{1}{|l}{\textbf{Special Forces Assistant Operations Manager (18F)}} & Washington and overseas                               & 2012-2018      \\
  \multicolumn{3}{|m{\linewidth}@{}}{%
  \begin{itemize}[leftmargin=*,nosep]
    \item Responsible for analysis and targeting to plan tactical operations for a Special Forces detachment.
    \item Regularly worked cooperatively with Iraqi, Philippine, Afghani, Korean, and Thai military partners.
    \item Gained working proficiency in Mandarin Chinese during two language exchange trips to Shenyang, China.
  \end{itemize}}                                               \\
\end{tabularx}

\vspace{-10px}
\section*{Skills}
\hrule
\begin{tabularx}{\linewidth}{@{}YYYYY@{}}
  C++             & Python & Javascript      & Node.js    & React          \\
  Typescript      & AWS    & Docker          & REST       & Postgres / SQL \\
  MongoDB / NoSQL & Git    & Jupyter / CoLab & Tensorflow & OpenCV         \\
\end{tabularx}

\vspace{-10px}
\section*{Education}
\hrule
\begin{tabularx}{\linewidth}{@{}XXr@{}}
  \textbf{M.S. Computer Science and Systems}     & University of Washington & December 2024 \\
  \textbf{B.S. Software Engineering}             & Arizona State University & 2022          \\
  \textbf{Intensive Second Year Chinese Program} & University of Washington & 2013          \\
\end{tabularx}
\end{document}