\documentclass[letterpaper,11pt]{article}
\usepackage[letterpaper, margin=0.5in]{geometry}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{mdframed}

\newcolumntype{Y}{>{\centering\arraybackslash}X}  
\setlength\parindent{0pt}
\pagestyle{empty}

\newmdenv[
  topline=false,
  bottomline=false,
  rightline=false,
  leftmargin=12pt,
  innerrightmargin=0pt,
  innerbottommargin=0pt,
  innertopmargin=0em,
  skipabove=\topsep,
  skipbelow=\topsep
]{leftrule}

\begin{document}
\begin{tabularx}{\linewidth}{@{}lYYr@{}}
  \multicolumn{4}{c}{\textbf{\Huge{James Kavanaugh}}}                                           \\
  \vspace{-10px}                                                                       &   &  & \\
  \hline
  \vspace{-10px}                                                                       &   &  & \\
  \faMapMarker*{ Seattle, WA}                                                          &
  \faPhone{ 253-209-9718}                                                              &
  \faEnvelope{ \href{mailto:jkav@northslopesoftware.com}{jkav@northslopesoftware.com}} &
  \faLinkedin{ \href{https://linkedin.com/in/jkav3}{linkedin.com/in/jkav3}}                     \\
  %\faGithub{ \href{https://github.com/dangerginger}{github.com/dangerginger}}                   \\
\end{tabularx}

\begin{mdframed}[backgroundcolor=gray!20,linewidth=0pt]
  \centering
  \textbf{\Large{Software Engineer}}
\end{mdframed}

\begin{center}
  \emph{Skilled bilingual software engineer with 20 years experience leading diverse high-performance teams.}
\end{center}

\vspace{-10px}
\section*{Projects}
\hrule
\begin{itemize}[leftmargin=*,nosep]
  \item \textbf{Marine construction permitting system}: Client relationship management (CRM) application implemented with Typescript, React, AWS, websockets, and MongoDB to manage multi-year permitting processes.
  \item \textbf{Web socket framework}: Typescript and Node.js web socket framework with message schema validation to enable real-time synchronization of web applications and maintain data consistency.
  \item \textbf{Encrypted synthetic data research}: Python and C++ based research using homomorphic encryption and differential privacy to maintain privacy of sensitive datasets while generating synthetic data.
  \item \textbf{Computer vision application}: C++, OpenCV and Tensorflow models to monitor RTSP camera streams, with macOS and tvOS client applications to view home security camera and insights.
        %\item \textbf{Request for quote application}: Cloud-native AWS application written in Typescript, React, Next.js that uses AWS Amplify, DynamoDB to streamline requesting and comparing vendor quotes.
        %\item \textbf{Space Time}: Native iOS and watchOS application with AWS Amplify and GraphQL backend to help users visualize time linearly instead of as a cycle to create urgency. Memento mori.
\end{itemize}

\vspace{-10px}
\section*{Experience}
\hrule
\begin{tabularx}{\linewidth}{@{}m{4in}Xr@{}}
  \textbf{President and CEO (Owner)} & North Slope Software & 2022-2024 \\
\end{tabularx}
\vspace{-1.5em}
\begin{itemize}[leftmargin=*,nosep]
  \item Responsible for product development, software engineering, user experience design, security, and DevOps.
  \item Designed and implemented a custom CRM application for a local marine construction company, which increased efficiency and reduced errors for the client saving \$50,000 over the product lifetime.
  \item Developed a websocket framework for the browser and Node.js to synchronize web applications with the backend data store to facilitate real-time collaboration between application users.
  \item Deployed web applications to AWS Amplify, EC2, S3, Route53, and other services to decrease fixed costs and increase reliability and scalability.
  \item Conducted business development with overseas software developers in India and Brazil to extend North Slope Software's capabilities and cut future development costs in half.
  \item Initiated customer and product development for a delegated awareness computer vision service for IP cameras using TensorFlow, AWS, Python, C++, Next.js, and DynamoDB.
\end{itemize}

\begin{tabularx}{\linewidth}{@{}m{4in}Xr@{}}
  \textbf{Master Sergeant, Green Beret, U.S. Army} & 1\textsuperscript{st} Special Forces Group (Airborne) & 2004-2024 \\
\end{tabularx}

\begin{leftrule}
  \begin{tabularx}{\linewidth}{@{}m{3.67in}Xr@{}}
    \textbf{Indo-Pacific Regional Program Manager (18Z)} & Washington and overseas & 2020-2024 \\
  \end{tabularx}
  \vspace{-1.75em}
  \begin{itemize}[leftmargin=*,nosep]
    \item Led a diverse multidisciplinary staff to manage joint special operations teams in seven Asian countries to counter regional adversaries and bolster American partnerships.
    \item Responsible for all advanced special operations in the Indo-Pacific theater, including 182 missions that increased achievement of military objectives by 200\%.
    \item Mentored and developed senior special operations leaders and technicians to achieve strategic effects and develop their careers.
    \item Translated high-level, ambiguous strategic guidance into achievable tactical tasks and supervised executing teams to ensure operations led to strategic results.
  \end{itemize}

  \begin{tabularx}{\linewidth}{@{}m{3.67in}Xr@{}}
    \textbf{Special Forces Team Sergeant (18Z)} & Washington and overseas & 2018-2020 \\
  \end{tabularx}
  \vspace{-1.75em}
  \begin{itemize}[leftmargin=*,nosep]
    \item Responsible for training, mentorship, and professional development of a high-performance and specialized Special Forces detachment.
    \item Acted as liaison between Special Operations Command (SOCOM), U.S. Government agencies, and Korean partners for combined operations to mitigate threats from regional adversaries.
  \end{itemize}

  \begin{tabularx}{\linewidth}{@{}m{3.67in}Xr@{}}
    \textbf{Special Forces Intelligence Sergeant (18F)} & Washington and overseas & 2012-2018 \\
  \end{tabularx}
  \vspace{-1.75em}
  \begin{itemize}[leftmargin=*,nosep]
    \item Responsible for analysis and planning to drive effective operations for a Special Forces detachment with limited guidance and resources in challenging environments.
    \item Conducted two Chinese language immersion and cultural exchange programs in Shenyang, China at Shenyang University and Liaoning University, gaining a working proficiency in Mandarin Chinese.
    \item Built trust and rapport with Iraqi, Philippine, Afghan, Korean, and Thai military partners to support combined operations on mutual goals.
  \end{itemize}

  \begin{tabularx}{\linewidth}{@{}m{3.67in}Xr@{}}
    \textbf{Special Forces Medical Sergeant (18D)} & Washington and overseas & 2007-2011 \\
  \end{tabularx}
  \vspace{-1.75em}
  \begin{itemize}[leftmargin=*,nosep]
    \item Conducted 150 combat patrols as the first responder for a Special Forces detachment and as a trainer and advisor for an Iraqi partner force to decrease deadly attacks, secure Tikrit, Iraq, and protect coalition forces.
    \item Sole medical provider running day-to-day operations for a clinic on the remote Jolo Island in the Philippines, providing medical and dental services by pulling teeth, treating infections, and more.
          %\item	Treated a patient with substantial electrical burns for four months, earning the the trust and respect of our Iraqi military partner force.

  \end{itemize}

  \begin{tabularx}{\linewidth}{@{}m{3.67in}Xr@{}}
    \textbf{Special Forces Recruit and Trainee (18X)} & Washington and overseas & 2004-2007 \\
  \end{tabularx}
\end{leftrule}

\section*{Skills}
\hrule
\begin{tabularx}{\linewidth}{@{}YYYYY@{}}
  C / C++         & Linux Admin & Debugging      & Data Structures & Algorithms \\
  Code Profiling  & Python      & Javascript     & Typescript      & Node.js    \\
  React / Next.js & AWS         & Postgres (SQL) & MongoDB (NoSQL) & Git        \\
\end{tabularx}

\vspace{-5px}
\section*{Education}
\hrule
\begin{tabularx}{\linewidth}{@{}XXr@{}}
  \textbf{M.S. Computer Science and Systems}     & University of Washington & December 2024 \\
  \textbf{B.S. Software Engineering}             & Arizona State University & 2022          \\
  \textbf{Intensive Second Year Chinese Program} & University of Washington & 2013          \\
\end{tabularx}
\end{document}