\documentclass[letterpaper,11pt]{article}
\usepackage[scale=0.9]{geometry}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{mdframed}

\newcolumntype{Y}{>{\centering\arraybackslash}X}  
\setlength\parindent{0pt}
\pagestyle{empty}

\begin{document}
\begin{tabularx}{\linewidth}{@{}lYcr@{}}                                                                      \\
  \multicolumn{4}{c}{\textbf{\Huge{James Kavanaugh}}}                                           \\
  \vspace{-10px}                                                                       &   &  & \\
  \hline
  \vspace{-10px}                                                                       &   &  & \\
  \faEnvelope{ \href{mailto:jkav@northslopesoftware.com}{jkav@northslopesoftware.com}} &
  \faPhone{ 253-209-9718}                                                              &
  \faLinkedin{ \href{https://linkedin.com/in/jkav3}{linkedin.com/in/jkav3}}            &
  \faGithub{ \href{https://github.com/dangerginger}{github.com/dangerginger}}                   \\
\end{tabularx}

\begin{mdframed}[backgroundcolor=gray!20,linewidth=0pt]
  \centering
  \textbf{\Large{Software Engineer}}
\end{mdframed}

\begin{center}
  \emph{Skilled bilingual software engineer with 20 years experience leading diverse high-performance teams.}
\end{center}

\vspace{-10px}
\section*{Projects}
\hrule
\begin{itemize}[leftmargin=*,nosep]
  \item \textbf{Marine construction permitting system}: Client relationship management (CRM) application implemented with Typescript, React, AWS, websockets, and MongoDB to manage multi-year permitting processes.
  \item \textbf{Web socket framework}: Typescript and Node.js web socket framework with message schema validation to enable real-time synchronization of web applications and maintain data consistency.
  \item \textbf{Encrypted synthetic data research}: Python and C++ based research using homomorphic encryption and differential privacy to maintain privacy of sensitive datasets while generating synthetic data.
  \item \textbf{Computer vision application}: C++, OpenCV and Tensorflow models to monitor RTSP camera streams, with macOS and tvOS client applications to view home security camera and insights.
  \item \textbf{Request for quote application}: Cloud-native AWS application written in Typescript, React, Next.js that uses AWS Amplify, DynamoDB to streamline requesting and comparing vendor quotes.
  \item \textbf{Space Time}: Native iOS and watchOS application with AWS Amplify and GraphQL backend to help users visualize time linearly instead of as a cycle to create urgency. Memento mori.
\end{itemize}

\vspace{-10px}
\section*{Experience}
\hrule
\begin{tabularx}{\linewidth}{@{}m{4in}Xr}
  \textbf{President and CEO (Owner)}                 & North Slope Software                                  & 2022-2024      \\
  \vspace{-10px}                                     & \vspace{-10px}                                        & \vspace{-10px} \\
  \multicolumn{3}{@{}m{\linewidth}}{%
  \begin{itemize}[leftmargin=*,nosep]
    \item Bootstrapped North Slope Software by providing compelling custom business applications to clients.
    \item Responsible for business development, user experience design, software development, and DevOps.
  \end{itemize}}                     \\
  \vspace{-20px}                                     & \vspace{-20px}                                        & \vspace{-20px} \\

  \textbf{U.S. Army Special Forces ``Green Berets''} & 1\textsuperscript{st} Special Forces Group (Airborne) & 2004-2024      \\
\end{tabularx}

\begin{mdframed}[backgroundcolor=white,linewidth=0.5pt,topline=false,rightline=false,bottomline=false,innerbottommargin=-15px,innerrightmargin=0px,innertopmargin=5px,innerleftmargin=5px,leftmargin=3px]
  \begin{tabularx}{\linewidth}{@{}m{3.85in}Xr}
    \textbf{Indo-Pacific Regional Program Manager (18Z)} & Washington and overseas & 2020-2024                           \\
    \multicolumn{3}{@{}m{\linewidth}@{}}{%
    \begin{itemize}[leftmargin=*,nosep]
      \item Led a diverse multifunctional staff to manage joint special operations teams in seven Asian countries.
      \item Mentored and developed leaders and technicians on high-performing teams to achieve strategic objectives.
      \item Responsible for written communication and briefings to synchronize operations with senior leaders' intent.
    \end{itemize}}      \\
    \vspace{-20px}                                       & \vspace{-20px}          & \vspace{-20px}                      \\

    \textbf{Operations Manager (18Z)}                    & Washington and overseas & 2018-2020                           \\
    \multicolumn{3}{@{}m{\linewidth}@{}}{%
    \begin{itemize}[leftmargin=*,nosep]
      \item Managed a high-performance, multifunctional, and highly specialized special forces detachment.
      \item Responsible for training, mentorship, and professional development for a Special Forces operational detachment.
    \end{itemize}} \\
    \vspace{-20px}                                       & \vspace{-20px}          & \vspace{-20px}                      \\

    \textbf{Assistant Operations Manager (18F)}          & Washington and overseas & 2012-2018                           \\
    \multicolumn{3}{m{\textwidth}@{}}{%
    \begin{itemize}[leftmargin=*,nosep]
      \item Responsible for data mining, analysis, and targeting to plan tactical operations for a Special Forces detachment.
      \item Worked cooperatively with Iraqi, Philippine, Afghani, Korean, and Thai military partners on mutual goals.
      \item Gained working proficiency in Mandarin Chinese during two language exchange trips to Shenyang, China.
    \end{itemize}}
  \end{tabularx}
\end{mdframed}

\vspace{-20px}
\section*{Skills}
\hrule
\begin{tabularx}{\linewidth}{@{}YYYYY@{}}
  Project Management & Communication & Agile Development & Strategic Planning & Machine Learning \\
  C / C++            & Python        & Javascript        & Typescript         & Node.js          \\
  React / Next.js    & AWS           & Postgres (SQL)    & MongoDB (NoSQL)    & Git              \\
\end{tabularx}

\vspace{-5px}
\section*{Education}
\hrule
\begin{tabularx}{\linewidth}{@{}XXr@{}}
  \textbf{M.S. Computer Science and Systems}     & University of Washington & December 2024 \\
  \textbf{B.S. Software Engineering}             & Arizona State University & 2022          \\
  \textbf{Intensive Second Year Chinese Program} & University of Washington & 2013          \\
\end{tabularx}
\end{document}